Ae. albopictus CPP manuscript

### 2020-01-24 GDDdata_input.Rmd
Ready for MS

---
title: "GDD Deadlines Japan/US 1998-2018"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

@@

```{r}
ggplot(filter(gdd400_all, year>2014), aes(x=latitude, y=gdd400, color=country)) + geom_point() + facet_wrap(~year)
```

@@

```{r}
tmin_us<-read.csv("AvgTmin_US.csv", check.names=FALSE) %>% gather(year, Tmin, "1998":"2018", factor_key=FALSE)
#In order to look at winter temperatures, need to combine Nov/Dec with Jan/Feb of the following year. January and February are reassigned in this table to the previous year to create seasonal years
tmin_us$year<-as.numeric(tmin_us$year) 
tmin_us$seasonalyear<-if_else(tmin_us$month %in% c("Jan","Feb"), tmin_us$year-1, tmin_us$year)
minwintertemp_us<-filter(tmin_us, month %in% c("Nov","Dec","Jan","Feb")) %>% group_by(pop, seasonalyear) %>% summarise(wintermin=min(Tmin)) %>% filter(!(seasonalyear %in% c(1997,2018)))
ggplot(minwintertemp_us, aes(x=seasonalyear, y=wintermin, color=pop)) + geom_point() + geom_line() + geom_vline(xintercept=c(2008,2018)) 
```
```{r}
tmin_jp<-read.csv("AvgTmin_JP.csv", check.names=FALSE) %>% gather(year, Tmin, "1998":"2018", factor_key=FALSE)
tmin_jp$year<-as.numeric(tmin_jp$year) 
tmin_jp$seasonalyear<-if_else(tmin_jp$month %in% c("Jan","Feb"), tmin_jp$year-1, tmin_jp$year)
minwintertemp_jp<-filter(tmin_jp, month %in% c("Nov","Dec","Jan","Feb")) %>% group_by(pop, seasonalyear) %>% summarise(wintermin=min(Tmin)) %>% filter(!(seasonalyear %in% c(1997,2018)))
ggplot(minwintertemp_jp, aes(x=seasonalyear, y=wintermin, color=pop)) + geom_point() + geom_line() + geom_vline(xintercept=c(2008,2018))
```

@@

```{r}
ggplot(filter(gdd400_all_new, year %in% c(2007,2017)), aes(x=latitude, y=wintermin, color=year)) + geom_point() + facet_grid(~country)

@@

```{r}
ggplot(filter(gdd400_all_new, year %in% c(2006,2016)), aes(x=latitude, y=wintermin, color=year)) + geom_point() + facet_grid(~country)

@@

```{r}
ggplot(filter(gdd400_all_new, year %in% c(2005,2015)), aes(x=latitude, y=wintermin, color=year)) + geom_point() + facet_grid(~country)

@@

```{r}
#adding 2008 and 2018 CPP values to big table of yearly deadlines and winter temps
cpp_year<-select(read.csv("cpp_calcs_filtered.csv"), pop, Estimate, year) %>% filter(year!="1988") %>% rename("CPP_YEAR"="year")
gdd400_all_new<-left_join(gdd400_all_new, cpp_year, by="pop")
gdd400_all_new$CPP_YEAR<-as.factor(gdd400_all_new2$CPP_YEAR)

@@

```{r}
ggplot(filter(gdd400_all_new, year %in% c(2007,2017)), aes(x=gdd400, y=Estimate, color=CPP_YEAR)) + scale_color_manual(values=c("gray", "black")) + geom_point() + facet_wrap(~year) + stat_smooth(method=lm)
```
```{r}
ggplot(filter(gdd400_all_new, year %in% c(2007,2017)), aes(x=wintermin, y=Estimate, color=CPP_YEAR)) + scale_color_manual(values=c("gray", "black")) + geom_point() + facet_wrap(~year) + stat_smooth(method=lm)
```

>>>>

---
title: "GDD Deadlines Japan/US 1998-2018"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

@@

```{r}
ggplot(filter(gdd400_all, year %in% c(2005, 2006, 2007, 2015, 2016, 2017)), aes(x=latitude, y=gdd400, color=country)) + geom_point() + facet_wrap(~year)
```

@@

```{r}
tmin_us<-read.csv("AvgTmin_US.csv", check.names=FALSE) %>% gather(year, Tmin, "1998":"2018", factor_key=FALSE)
#In order to look at winter temperatures, need to combine Nov/Dec with Jan/Feb of the following year. January and February are reassigned in this table to the previous year to create seasonal years
tmin_us$year<-as.numeric(tmin_us$year) 
tmin_us$seasonalyear<-if_else(tmin_us$month %in% c("Jan","Feb"), tmin_us$year-1, tmin_us$year)
minwintertemp_us<-filter(tmin_us, month %in% c("Nov","Dec","Jan","Feb")) %>% group_by(pop, seasonalyear) %>% summarise(wintermin=min(Tmin), wintermonths_sd=sd(Tmin)) %>% filter(!(seasonalyear %in% c(1997,2018)))
ggplot(minwintertemp_us, aes(x=seasonalyear, y=wintermin, color=pop)) + geom_point() + geom_line() + geom_vline(xintercept=c(2008,2018)) 
```
```{r}
ggplot(minwintertemp_us, aes(x=seasonalyear, y=wintermonths_sd, color=pop)) + geom_point() + geom_line() + geom_vline(xintercept=c(2008,2018))

```{r}
tmin_jp<-read.csv("AvgTmin_JP.csv", check.names=FALSE) %>% gather(year, Tmin, "1998":"2018", factor_key=FALSE)
tmin_jp$year<-as.numeric(tmin_jp$year) 
tmin_jp$seasonalyear<-if_else(tmin_jp$month %in% c("Jan","Feb"), tmin_jp$year-1, tmin_jp$year)
minwintertemp_jp<-filter(tmin_jp, month %in% c("Nov","Dec","Jan","Feb")) %>% group_by(pop, seasonalyear) %>% summarise(wintermin=min(Tmin), wintermonths_sd=sd(Tmin)) %>% filter(!(seasonalyear %in% c(1997,2018)))
ggplot(minwintertemp_jp, aes(x=seasonalyear, y=wintermin, color=pop)) + geom_point() + geom_line() + geom_vline(xintercept=c(2008,2018))
```
```{r}
ggplot(minwintertemp_jp, aes(x=seasonalyear, y=wintermonths_sd, color=pop)) + geom_point() + geom_line() + geom_vline(xintercept=c(2008,2018))

@@

```{r}
ggplot(filter(gdd400_all_new, year %in% c(2007,2017), only_2008=="n"), aes(x=latitude, y=wintermin, color=as.factor(year))) + geom_point() + facet_grid(~country) + scale_color_manual(values=c("blue","orange"))

@@

```{r}
ggplot(filter(gdd400_all_new, year %in% c(2006,2016), only_2008=="n"), aes(x=latitude, y=wintermin, color=as.factor(year))) + geom_point() + facet_grid(~country) + scale_color_manual(values=c("blue","orange"))

@@

```{r}
ggplot(filter(gdd400_all_new, year %in% c(2005,2015)), aes(x=latitude, y=wintermin, color=as.factor(year))) + geom_point() + facet_grid(~country) + scale_color_manual(values=c("blue","orange"))

@@

```{r}
#adding 2008 and 2018 CPP values to big table of yearly deadlines and winter temps
cpp_year<-select(read.csv("cpp_calcs_filtered.csv"), pop, Estimate, year) %>% filter(year!="1988") %>% rename("CPP_YEAR"="year")
gdd400_all_new<-left_join(gdd400_all_new, cpp_year, by="pop")
gdd400_all_new$CPP_YEAR<-as.factor(gdd400_all_new$CPP_YEAR)

@@

# 2008 and 2018 CPP estimates vs GDD deadline

```{r}

ggplot(filter(gdd400_all_new, year==2007, CPP_YEAR==2018), aes(x=gdd400, y=Estimate, color=country)) + geom_point() + stat_smooth(method=lm) 
```
```{r}
ggplot(filter(gdd400_all_new, year==2007, CPP_YEAR==2018), aes(x=latitude, y=Estimate, color=country)) + geom_point() + stat_smooth(method=lm)

```{r}
ggplot(filter(gdd400_all_new, year %in% c(2007,2017)), aes(x=gdd400, y=Estimate, color=CPP_YEAR)) + scale_color_manual(values=c("gray", "black")) + geom_point() + facet_wrap(~year) + stat_smooth(method=lm)
```

# Variability (SD) in winter coldness in 1998-2007 vs. 2008-2017

```{r}
variation_summary<-filter(gdd400_all_new, interval!="NA", CPP_YEAR=="2018") %>% group_by(pop, interval) %>% dplyr::summarize(lat=mean(latitude), country=first(country), gdd400_sd=sd(gdd400), wintermin_sd=sd(wintermin), cpp_2018=mean(Estimate))
ggplot(variation_summary, aes(x=lat, y=wintermin_sd, color=interval)) + geom_point() + facet_grid(~country)
```

### 2020-01-24 MS.Rmd
Ready for MS

```{r eval=FALSE, message=FALSE, include=FALSE}
install.packages("tidyverse") #1.2.1
install.packages("drc") #3.0.1
install.packages("stringr")
install.packages("geosphere")
install.packages("lubridate")
install.packages(c("maps", "mapdata"))
devtools::install_github("dkahle/ggmap")
install.packages("scatterpie")
install.packages("ggedit")
install.packages("ggrepel")
install.packages("papeR")
install.packages("cowplot")

@@

```{r DI_plot, echo=FALSE, include=FALSE}
#plot with DI at 8 h shown as TWO DIFFERENT points (corresponding to two cabinets)
c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK")
DI_summary$pop<-factor(DI_summary$pop, levels=c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK"))
DI_plot<-ggplot(DI_summary, aes(x=pp, y=DI, group=pop)) + geom_point() + facet_wrap(~pop) + theme_bw() + xlab("Photoperiod (hours)") + ylab("Dipause incidence")

@@

```{r}

@@

>>>>

```{r eval=FALSE, message=FALSE, include=FALSE}
install.packages("tidyverse") #1.2.1
install.packages("drc") #3.0.1
install.packages("stringr")
install.packages("geosphere")
install.packages("lubridate")
install.packages(c("maps", "mapdata"))
devtools::install_github("dkahle/ggmap")
install.packages("scatterpie")
install.packages("ggedit")
install.packages("ggrepel")
install.packages("papeR")
install.packages("cowplot")
```

@@

```{r DI_plot, echo=FALSE, include=FALSE}
#plot with DI at 8 h shown as TWO DIFFERENT points (corresponding to two cabinets)
c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK")
DI_summary$pop<-factor(DI_summary$pop, levels=c("PBS", "FEM", "OAK", "JAC", "BRU", "ZIO", "FAY", "NVA", "WAV", "MAN", "BER", "NEW", "OKI", "TAN", "KAG", "YAT", "SAG", "SHI", "YAM", "HIR", "KYO", "TAK", "TOK", "UTS", "KAN", "KHO", "AIZ", "NIG", "SEN", "SAK"))
DI_plot<-ggplot(DI_summary, aes(x=pp, y=DI, group=pop)) + geom_point() + facet_wrap(~fct_reorder(pop, lat)) + theme_bw() + xlab("Photoperiod (hours)") + ylab("Dipause incidence")

@@

@@

```{r}
```
